---
title: "ACREP Updated Analyses"
author: "erin buchanan"
date: "Last Updated `r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 15)
```

## Update:

This file is the same for all analyses presented this folder - separated out so it could be run without repeating in each file and making mistakes on the processing. 

## Information

Multilab close replication of: Experiment 1 from Turri, J., Buckwalter, W., & Blouw, P. (2015). Knowledge and luck. *Psychonomic Bulletin and Review*, 22, 378-390.

[Data and registered protocols:](https://osf.io/n5b3w/)

[Codebook (raw data)](https://docs.google.com/spreadsheets/d/1KjXqgfVgguHeDXVtlHHhJ9zsRGVDfPVPH4tbh75P46U/edit#gid=903093128)

[Preprint](https://psyarxiv.com/zeux9/)

## Libraries

```{r}
library(rio)
library(lme4)
library(lmerTest)
library(nlme)
library(MuMIn)
library(plyr)
library(psych)
library(tidyr)
library(ggplot2)
library(dplyr)
library(ggmosaic)
library(MOTE)
library(flextable)
library(RColorBrewer)
```

## Import the Data

The `full_long` dataset includes all participants in long format - wherein each trial of their study is on one row of the dataset. Our uploaded data also includes `full.Rds` which is the same data in wide format - one column for each variable in the dataset and one row per participant.

```{r}
full_long <- readRDS("../04_Data/rds/d_all_long.Rds")
#str(full_long)
```

## Open Ended Response Coding 

Import the open-ended responses and prepare them for merging with the final dataset. This section:

  - Imports all the files
  - Includes a coder id
  - Corrects all the issues with typed codings
  - Converts each item to coder counts so you can convert from wide to long
  - Converts from wide to long
  - Converts into scoring:
    - No or NA gets 0 points 
    - Maybe gets 1 point
    - Yes/test gets 2 points
    - Participants are marked as "excluded" if they get 4 total points across three coders 
  - Participants are also marked as "nonsense" if they did not write a legible answer or simply typed gibberish. These data points are not excluded but marked if you would like to repeat the analysis and exclude them. 

```{r}
file.names <- list.files(path = "../04_Data/open_responses/", 
                         pattern = ".xlsx", full.names = T, 
                         recursive = T)

previous.files <- lapply(file.names, function(x){ import(x, sheet = 2)})
purpose.files <- lapply(file.names, function(x){ import(x, sheet = 3)})

# add coder ids 
coder.id <- unlist(lapply(strsplit(file.names, "psa004"), function(x) x[[2]]))

names(previous.files) <- coder.id
names(purpose.files) <- coder.id

previousDF <- do.call(rbind.fill, previous.files)
purposeDF <- do.call(rbind.fill, purpose.files)

previousDF$coder <- rep(names(previous.files), unlist(lapply(previous.files, nrow)))
purposeDF$coder <- rep(names(purpose.files), unlist(lapply(purpose.files, nrow)))

# ensure the text is normalized 
previousDF$previous <- gsub("\\s+", " ", previousDF$previous)
purposeDF$purpose <- gsub("\\s+", " ", purposeDF$purpose)
previousDF$previous <- gsub("\\s$", "", previousDF$previous)
purposeDF$purpose <- gsub("\\s$", "", purposeDF$purpose)

# can't figure out why these two are different
purposeDF$purpose[purposeDF$id == "s10313"] <- "I'm not sure."
purposeDF$purpose[purposeDF$id == "s10513"] <- "Recall, recognizing"

# fix the yes/no/maybe/NA
previousDF$code <- tolower(previousDF$code)
table(previousDF$code)
previousDF$code <- gsub("np", "no", previousDF$code)
previousDF$code <- gsub("n/a", "na", previousDF$code)
previousDF$code <- gsub("y$", "yes", previousDF$code)
table(previousDF$code)
previousDF <- subset(previousDF, !is.na(id))

purposeDF$code <- tolower(purposeDF$code)
table(purposeDF$code)
purposeDF$code <- gsub("mayb$|meybe", "maybe", purposeDF$code)
purposeDF$code <- gsub("mo", "no", purposeDF$code)
purposeDF$code <- gsub("n/a", "na", purposeDF$code)
table(purposeDF$code)
purposeDF <- subset(purposeDF, !is.na(id))

# add coder count
previous_count <- as.data.frame(table(previousDF$id))
previous_count <- previous_count[order(previous_count$Var1), ]
previousDF <- previousDF[order(previousDF$id), ]
previousDF$coder_num <- NA

for (i in 1:length(previous_count$Freq)){
  previousDF$coder_num[previousDF$id == previous_count$Var1[i]] <- 1:previous_count$Freq[i]
}

purpose_count <- as.data.frame(table(purposeDF$id))
purpose_count <- purpose_count[order(purpose_count$Var1), ]
purposeDF <- purposeDF[order(purposeDF$id), ]
purposeDF$coder_num <- NA

for (i in 1:length(purpose_count$Freq)){
  purposeDF$coder_num[purposeDF$id == purpose_count$Var1[i]] <- 1:purpose_count$Freq[i]
}

# long to wide for scoring
previousDF_wide <- pivot_wider(data = previousDF,
                              id_cols = c("id", "survey_lang", "previous"), 
                              names_from = "coder_num",
                              values_from = "code")

purposeDF_wide <- pivot_wider(data = purposeDF,
                              id_cols = c("id", "survey_lang", "purpose"), 
                              names_from = "coder_num",
                              values_from = "code")

# score the yes/no/maybe/NA
previousDF_wide$score_1 <- previousDF_wide$`1`
previousDF_wide$score_2 <- previousDF_wide$`2`
previousDF_wide$score_3 <- previousDF_wide$`3`

previousDF_wide$score_1 <- gsub("maybe", "1", previousDF_wide$score_1)
previousDF_wide$score_1 <- gsub("no|na", "0", previousDF_wide$score_1)
previousDF_wide$score_1 <- gsub("yes|test", "2", previousDF_wide$score_1)
previousDF_wide$score_2 <- gsub("maybe", "1", previousDF_wide$score_2)
previousDF_wide$score_2 <- gsub("no|na", "0", previousDF_wide$score_2)
previousDF_wide$score_2 <- gsub("yes|test", "2", previousDF_wide$score_2)
previousDF_wide$score_3 <- gsub("maybe", "1", previousDF_wide$score_3)
previousDF_wide$score_3 <- gsub("no|na", "0", previousDF_wide$score_3)
previousDF_wide$score_3 <- gsub("yes|test", "2", previousDF_wide$score_3)

previousDF_wide$count <- apply(
  previousDF_wide[ , grep("score", colnames(previousDF_wide))], 1, 
  function(x) { sum(!is.na(x)) } )
previousDF_wide$sum <- apply(
  previousDF_wide[ , grep("score", colnames(previousDF_wide))], 1, 
  function (x) { sum(as.numeric(x), na.rm = T)} )

previousDF_wide$exclude <- previousDF_wide$sum >= 4
previousDF_wide$nonsense <- apply(
  previousDF_wide[ , grep("1|2|3|4", colnames(previousDF_wide))], 1, 
  function (x) {sum(as.numeric(x == "na"), na.rm = T)}
) == 3

purposeDF_wide$score_1 <- purposeDF_wide$`1`
purposeDF_wide$score_2 <- purposeDF_wide$`2`
purposeDF_wide$score_3 <- purposeDF_wide$`3`

purposeDF_wide$score_1 <- gsub("maybe", "1", purposeDF_wide$score_1)
purposeDF_wide$score_1 <- gsub("no|na", "0", purposeDF_wide$score_1)
purposeDF_wide$score_1 <- gsub("yes|test", "2", purposeDF_wide$score_1)
purposeDF_wide$score_2 <- gsub("maybe", "1", purposeDF_wide$score_2)
purposeDF_wide$score_2 <- gsub("no|na", "0", purposeDF_wide$score_2)
purposeDF_wide$score_2 <- gsub("yes|test", "2", purposeDF_wide$score_2)
purposeDF_wide$score_3 <- gsub("maybe", "1", purposeDF_wide$score_3)
purposeDF_wide$score_3 <- gsub("no|na", "0", purposeDF_wide$score_3)
purposeDF_wide$score_3 <- gsub("yes|test", "2", purposeDF_wide$score_3)

purposeDF_wide$count <- apply(
  purposeDF_wide[ , grep("score", colnames(purposeDF_wide))], 1, 
  function(x) { sum(!is.na(x)) } )
purposeDF_wide$sum <- apply(
  purposeDF_wide[ , grep("score", colnames(purposeDF_wide))], 1, 
  function (x) { sum(as.numeric(x), na.rm = T)} )

purposeDF_wide$exclude <- purposeDF_wide$sum >= 4
purposeDF_wide$nonsense <- apply(
  purposeDF_wide[ , grep("1|2|3", colnames(purposeDF_wide))], 1, 
  function (x) {sum(as.numeric(x == "na"), na.rm = T)}
) == 3

sum(duplicated(purposeDF_wide$id))
#ids <- purposeDF_wide$id[duplicated(purposeDF_wide$id)]
#View(purposeDF_wide[purposeDF_wide$id %in% ids, ])
sum(duplicated(previousDF_wide$id))
#ids <- previousDF_wide$id[duplicated(previousDF_wide$id)]
#View(previousDF_wide[previousDF_wide$id %in% ids, ])
```

### Finding missing coders:

```{r}
previous_missing <- subset(previousDF_wide, count < 3)
purpose_missing <- subset(purposeDF_wide, count < 3)

table(previous_missing$survey_lang)
table(purpose_missing$survey_lang)

#create reviewer names
previous_completed <- previousDF %>% 
  group_by(id) %>% 
  summarize(coder = paste(coder, collapse = ", "))

purpose_completed <- purposeDF %>% 
  group_by(id) %>% 
  summarize(coder = paste(coder, collapse = ", "))

previous_missing <- merge(previous_missing, 
                          previous_completed, 
                          by = "id", 
                          all.x = T)

purpose_missing <- merge(purpose_missing, 
                         purpose_completed,
                         by = "id", 
                         all.x = T)

write.csv(previous_missing, "../04_Data/data/previous_needs.csv", row.names = F)
write.csv(purpose_missing, "../04_Data/data/purpose_needs.csv", row.names = F)
```

```{r}
previousDF_long_missing <- subset(previousDF, id %in% previous_missing$id)
previousDF_wide_missing <- pivot_wider(data = previousDF_long_missing, 
                                       id_cols = c("id", "survey_lang"), 
                                       values_from = "code", 
                                       names_from = "coder")

purposeDF_long_missing <- subset(purposeDF, id %in% purpose_missing$id)
purposeDF_wide_missing <- pivot_wider(data = purposeDF_long_missing, 
                                       id_cols = c("id", "survey_lang"), 
                                       values_from = "code", 
                                       names_from = "coder")

write.csv(previousDF_wide_missing, "../04_Data/data/previous_needs_wide.csv", row.names = F)
write.csv(purposeDF_wide_missing, "../04_Data/data/purpose_needs_wide.csv", row.names = F)
```

## Fix Data Coding / Examine Covariates  

### Deal with lab coding issues:

  - Import lab sheet
  - Delete cases that should not be used 

```{r} 
lab_sheet <- import("../04_Data/data/lab_sheet_un_region_update.csv") %>%
  select(-un_region2)

nrow(full_long)

setdiff(unique(full_long$lab_id), lab_sheet$lab_code)
setdiff(lab_sheet$lab_code, unique(full_long$lab_id))

# delete test and do not use cases
full_long <- subset(full_long, lab_id %in% lab_sheet$lab_code[lab_sheet$use == "Yes"])

nrow(full_long)
str(full_long$lab_id)

full_long$lab_id <- droplevels(full_long$lab_id)
```

### Deal with compensation issues:

  - Deal with compensation for labs with no information because they didn't see that question
  
```{r}
# deal with compensation questions
# give compensation type labels
table(full_long$comp, useNA = "ifany")
full_long$comp <- factor(full_long$comp,
                         levels = 1:3,
                         labels = c("No", "Yes", "Not Sure"))

# examine compensation type by lab
table(full_long$lab_id, full_long$comp, useNA = "ifany")

# find labs that had majority no comp
lab_comp_temp <- as.data.frame(table(full_long$lab_id, full_long$comp, useNA = "ifany") / rowSums(table(full_long$lab_id, full_long$comp, useNA = "ifany")) * 100)

lab_comp_temp <- lab_comp_temp[order(lab_comp_temp$Freq, decreasing = T) , ]
lab_comp_max <- lab_comp_temp[!duplicated(lab_comp_temp$Var1), ]
lab_comp_max <- subset(lab_comp_max, is.na(Var2))
colnames(lab_comp_max) <- c("lab_code", "comp", "Percent")

# clean up lab codes compensation
table(lab_sheet$compensation, useNA = "ifany")
lab_sheet$comp <- lab_sheet$compensation
lab_sheet$comp <- gsub("Course Credit for Students, Nothing for Community", "Mixed", lab_sheet$comp)
lab_sheet$comp <- gsub("Course Credit|Lottery|Money|Sweets|Course Credit, Money", "Yes", lab_sheet$comp)
lab_sheet$comp <- gsub("None", "No", lab_sheet$comp)

table(lab_sheet$comp, useNA = "ifany")

# merge these two things together
lab_comp_max <- merge(lab_comp_max, lab_sheet, by = "lab_code")

# drop all unclear or mixed
lab_comp_max <- subset(lab_comp_max, comp.y != "Mixed" & 
                         comp.y != "Unclear")

# fix compensation for labs 
full_long$comp[full_long$lab_id %in% 
                 lab_comp_max$lab_code[lab_comp_max$comp.y == "Yes"]] <- "Yes"
full_long$comp[full_long$lab_id %in% 
                 lab_comp_max$lab_code[lab_comp_max$comp.y == "No"]] <- "No"

table(full_long$lab_id, full_long$comp, useNA = "ifany") 

# deal with not sures 
table(full_long$comp, useNA = "ifany")

# if they wrote not sure 
# and didn't pick one of the compensation options
# then they did not get compensated
full_long$comp[full_long$comp == "Not Sure" & is.na(full_long$comp_type)] <- "No"

# if they wrote note sure
# but then picked a compensation option
# then the answer is yes 
full_long$comp[full_long$comp == "Not Sure" & !is.na(full_long$comp_type)] <- "Yes"

#add turk variable
full_long$turk <- full_long$lab_id == "b6c8ec"

full_long$comp <- droplevels(full_long$comp)
```

### Fix Lab ID to Consistent "Data Collection Location ID"

```{r}
full_long <- merge(full_long, 
                   lab_sheet[ , c("lab_code", "un_region", "person_code")],
                   by.x = "lab_id", by.y = "lab_code", 
                   all.x = T)

table(full_long$person_code)
nrow(full_long)
```

### Examine Coding for Covariates 

  - Examine gender labels
  - Recode education to number and examine ... fix issues with two labs not using the same education values.

```{r}
# better labels for graphs
full_long$vignette <- factor(full_long$vignette,
                             levels = c("D", "E", "G"),
                             labels = c("Darrel", "Emma", "Gerald"))

full_long$cond <- factor(full_long$cond,
                             levels = c("G", "I", "K"),
                             labels = c("Gettier", "Ignorance", "Knowledge"))

# gender
table(full_long$gender, useNA = "ifany")

# describe education years
full_long$education <- as.numeric(full_long$education)
describe(full_long$education[!duplicated(full_long$id)])

levels(full_long$education_level)

# less high school = 10  
# high school = 12
# some college = 14
# college = 16
# masters = 18
# graduate = 20

# levels(full_long$education) <- c(levels(full_long$education), 20, 21)
# truncate all education since that's how it was on socisurvey

full_long$education[full_long$education_level == "Less than high school" & !is.na(full_long$education_level)] <- 10
full_long$education[full_long$education_level == "High school diploma (or GED)" & !is.na(full_long$education_level)] <- 12
full_long$education[full_long$education_level == "Some college or a 2-year college degree (A.A.)" & !is.na(full_long$education_level)] <- 14
full_long$education[full_long$education_level == "4-year college degree (B.A., B.S.)" & !is.na(full_long$education_level)] <- 16
full_long$education[full_long$education_level == "Master’s degree (M.A., M.S.)" & !is.na(full_long$education_level)] <- 18 #> 17 group
full_long$education[full_long$education_level == "Graduate or professional degree (J.D., Ph.D., M.D.)" & !is.na(full_long$education_level)] <-  18 #>17 group

# PRT lab bach = 15, master = 17, PHD = 21
full_long$education[full_long$education_level == "4-year college degree (B.A., B.S.)" & !is.na(full_long$education_level) & full_long$lab_id == "b6c8ec"] <- 14
full_long$education[full_long$education_level == "Master’s degree (M.A., M.S.)" & !is.na(full_long$education_level) & full_long$lab_id == "b6c8ec"] <- 17
full_long$education[full_long$education_level == "Graduate or professional degree (J.D., Ph.D., M.D.)" & !is.na(full_long$education_level) & full_long$lab_id == "b6c8ec"] <-  18 #> 17 group 

# describe age
describe(full_long$age[!duplicated(full_long$id)])

# number of rows
nrow(full_long)
# number of participants
length(unique(full_long$id))
# number of data collection locations
length(unique(full_long$person_code))
```

## Write Out

```{r}
save(full_long, file = "clean_full_long.Rdata")
save(previousDF_wide, file = "previousDF_wide.Rdata")
save(purposeDF_wide, file = "purposeDF_wide.Rdata")
```

