---
title: "Analysis: Linear with Original Exclusions"
author: "erin buchanan"
date: "Last Updated `r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 15)
```

## Update

Note: a good amount of code is eliminated to make this run faster. 

## Libraries

```{r}
library(rio)
library(lme4)
library(lmerTest)
library(nlme)
library(MuMIn)
library(plyr)
library(psych)
library(tidyr)
library(ggplot2)
library(dplyr)
library(ggmosaic)
library(MOTE)
library(flextable)
library(RColorBrewer)
```

## Load Data Clean Up

```{r}
load("clean_full_long.Rdata")
load("previousDF_wide.Rdata")
load("purposeDF_wide.Rdata")
```

## Study Exclusions

In this section, we will mark each exclusion criteria to be able to denote how many exclusions each participant may have had.

### Majority Age

(1) if the participant is not the majority age of their country or older (unless parent/guardian waiver provided)

In this section, we will exclude all participants who are under 18 or are not the majority age of their country or older.

https://en.wikipedia.org/wiki/Age_of_majority

```{r}
# table of lab countries
full_long$lab_country <- droplevels(full_long$lab_country)
table(full_long$lab_country, useNA = "ifany")

# age information
summary(full_long$age)

# minimum age by country
tapply(full_long$age, full_long$lab_country, min, na.rm = T)

# exclude based on age
full_long$age_exclusion <- NA

# everyone under 18
full_long$age_exclusion <- full_long$age < 18

# everyone over 100 
# full_long$age_exclusion[full_long$age > 100] <- TRUE

# TWN age of majority is 20 at time of study
full_long$age_exclusion[full_long$lab_country %in% "TWN"] <- full_long$age[full_long$lab_country %in% "TWN"] < 20
```

### Previous Knowledge/Participation of Study 

(2) if the participant has taken part in a previous version of this study or in another contributors' replication of the same study

```{r}
full_long <- merge(full_long,
                   previousDF_wide[ , c("id", "exclude", "nonsense")], all.x = T) 

# number of rows
nrow(full_long)
# number of participants
length(unique(full_long$id))

colnames(full_long)[(ncol(full_long)-1):ncol(full_long)] <- c("previous_exclusion", "previous_nonsense")

full_long$previous_exclusion[full_long$previous == ""] <- FALSE
full_long$previous_nonsense[full_long$previous == ""] <- FALSE
full_long$previous_exclusion[is.na(full_long$previous)] <- FALSE
full_long$previous_nonsense[is.na(full_long$previous)] <- FALSE
full_long$previous_exclusion[nchar(full_long$previous) < 2] <- FALSE
full_long$previous_nonsense[nchar(full_long$previous) < 2] <- FALSE
```

### Comprehension Questions 

(3) if the participant fails to answer comprehension questions correctly

```{r}
table(full_long$dge_valid)

full_long$studyans_exclusion <- !(full_long$dge_valid)

table(full_long$compr, full_long$vignette)
```

### Knowledge of Experiment/Hypothesis 

(4) if the participant correctly and explicitly articulate knowledge of the specific hypotheses or specific conditions of this study when answering the funneled debriefing questions. 

```{r}
full_long <- merge(full_long,
                   purposeDF_wide[ , c("id", "exclude", "nonsense")], all.x = T) 

# number of rows
nrow(full_long)
# number of participants
length(unique(full_long$id))

colnames(full_long)[(ncol(full_long)-1):ncol(full_long)] <- c("purpose_exclusion", "purpose_nonsense")

full_long$purpose_exclusion[full_long$purpose == ""] <- FALSE
full_long$purpose_nonsense[full_long$purpose == ""] <- FALSE
full_long$purpose_exclusion[is.na(full_long$purpose)] <- FALSE
full_long$purpose_nonsense[is.na(full_long$purpose)] <- FALSE
full_long$purpose_exclusion[nchar(full_long$purpose) < 2] <- FALSE
full_long$purpose_nonsense[nchar(full_long$purpose) < 2] <- FALSE 
```

### Language Proficiency 

We will also exclude participants who self-report their understanding of the tested language as "not well" or "not well at all". We based this exclusion criteria on a recent study that found that non-native English speakers who self-report as "very well" and "well" tend to score in the "intermediate" and "basic" categories on an English proficiency test respectively, while those who self-report as "not well" and "not at all" tend to score in the "below basic" category (Vickstrom, Shin, Collazo, & Bauman, 2015). All excluded data will be included in the data files on the overall OSF page, along with the particular reason for why they were excluded. 

```{r}
summary(full_long$language)

full_long$lang_exclusion <- full_long$language == "not very well" | full_long$language == "not well at all" 
```

### Exclude Non-Finishing Teams

```{r}
full_long$team_exclusion <- full_long$completed_crep_requirements == "Yes"
```

### Total Exclusions

In this section, we provide the total (data point) exclusions for each particular screening item plus a table with all exclusions forever. 

```{r}
# exclusions individually
table(full_long$age_exclusion, useNA = "ifany") / 3
table(full_long$lang_exclusion, useNA = "ifany") / 3
table(full_long$studyans_exclusion, useNA = "ifany") / 3
table(full_long$previous_exclusion, useNA = "ifany") / 3
table(full_long$purpose_exclusion, useNA = "ifany") / 3 
table(full_long$team_exclusion, useNA = "ifany") / 3

# for these, NA means they should be excluded
full_long$age_exclusion[is.na(full_long$age_exclusion)] <- TRUE
full_long$lang_exclusion[is.na(full_long$lang_exclusion)] <- TRUE
full_long$studyans_exclusion[is.na(full_long$studyans_exclusion)] <- TRUE

# for these, NA means no answer which is ok 
full_long$previous_exclusion[is.na(full_long$previous_exclusion)] <- FALSE
full_long$purpose_exclusion[is.na(full_long$purpose_exclusion)] <- FALSE

full_long$total_exclusion <- apply(full_long[ , grep("exclusion", colnames(full_long))], 1, sum, na.rm = T)

table(full_long$total_exclusion, useNA = "ifany") / 3

# multiway table of all exclusions 
exclusions <- as.data.frame(table(full_long$age_exclusion, 
                                  full_long$lang_exclusion, 
                                  full_long$previous_exclusion,
                                  full_long$purpose_exclusion, 
                                  full_long$studyans_exclusion,
                                  full_long$team_exclusion, 
                                  useNA = "ifany"))
colnames(exclusions) <- c("Age", "Language", "Previous", "Purpose", "Comprehension", "Team Exclusion", "Frequency")
exclusions$Num_Participants <- exclusions$Frequency / 3

exclusions

final_long <- subset(full_long, total_exclusion < 1)

# drop all the levels that no longer exist within the data 
final_long <- droplevels(final_long)

# total number data points originally
nrow(full_long) 
# total number data points now
nrow(final_long) 

# original number of participants 
length(unique(full_long$id)) 
# final number of participants 
length(unique(final_long$id)) 
```

## Code We Need

```{r}
final_long$bin_order <- droplevels(final_long$bin_order)

# drop levels
final_long$id <- factor(final_long$id)
final_long$vignette <- factor(final_long$vignette)

# for luck analyses people should be excluded if they get the answer wrong 
final_long$luck_correct <- FALSE

final_long$ri_wr <- factor(final_long$ri_wr, 
                           levels = c(1,2),
                           labels = c("Right", "Wrong"))
final_long$luck_correct[final_long$cond == "Ignorance" & final_long$ri_wr == "Wrong"] <- TRUE
final_long$luck_correct[final_long$cond != "Ignorance" & final_long$ri_wr == "Right"] <- TRUE

# subset the wrong answers 
final_luck <- subset(final_long, luck_correct)

final_long$bin_order <- droplevels(final_long$bin_order)
```

### Gender Other

Because of the small other category, we will simply compare male to female. 

```{r}
final_long$gender2 <- factor(final_long$gender,
                             levels = c("female", "male"))

final_luck$gender2 <- factor(final_luck$gender,
                             levels = c("female", "male"))

table(final_long$gender, useNA = "ifany")
table(final_long$gender2, useNA = "ifany")
```

```{r}
final_long$id <- droplevels(final_long$id)
```

## Final Analysis Knowledge

### Model 1 

Intercept only model to help determine if the addition of random intercepts are useful.

```{r}
k.model.1 <- glm(know_vas ~ 1,
               data = final_long,
               
               na.action = "na.omit")
```

### Model 2

Vignette random intercept model:

```{r}
k.model.2 <- lmer(know_vas ~ (1|vignette),
                      data = final_long,
                  na.action = "na.omit")
```

### Model 3

Vignette nested in participants random intercept:

```{r}
# k.model.3 <- lmer(know_vas ~ (1|vignette/id),
#                       data = final_long,
#                   na.action = "na.omit")
# can't do this 
```
  
### Model 4

Vignette nested in participants which is then nested in labs:

```{r}
k.model.4 <- lmer(know_vas ~ (1|vignette/person_code),
                      data = final_long,
                  na.action = "na.omit")
```
  
### Model 5

Addition of the covariates added to the vignette random intercept model. 

```{r}
k.model.5 <- lmer(know_vas ~ (1|vignette/person_code) + 
                   comp + age + gender2 + education,
                      data = final_long,
                  na.action = "na.omit")
```
  
### Model 6

The previous model of covariates plus the variable of focus: condition.

```{r}
k.model.6 <- lmer(know_vas ~ (1|vignette/person_code) + 
                   comp + age + gender2 + education + 
                   cond,
                      data = final_long,
                  na.action = "na.omit")
```

### Model 6A

Does the vignette interact with the condition?

```{r}
k.model.6A <- lmer(know_vas ~ (1 | vignette/person_code) + 
                   comp + age + gender2 + education + 
                   cond*vignette,
                      data = final_long,
                  na.action = "na.omit")
```

### Model 6B

Data was collected from mechanical turk participants. Are there differences in this data and the complete data on the condition variable? 

```{r}
k.model.6B <- lmer(know_vas ~ (1|vignette/person_code) + 
                    comp + age + gender2 + education + 
                    cond*turk,
                      data = final_long,
                  na.action = "na.omit")
```
  
## Final Analysis Reasonableness

### Model 1 

Intercept only model to help determine if the addition of random intercepts are useful.

```{r}
#scores should be 0 and 1 for this analysis 
final_long$reason_vas <- final_long$reason_vas - 1

r.model.1 <- glm(reason_vas ~ 1,
               data = final_long,
                  na.action = "na.omit")
```

### Model 2

Vignette random intercept model:

```{r}
r.model.2 <- lmer(reason_vas ~ (1|vignette),
                      data = final_long,
                  na.action = "na.omit")
```
  
### Model 3

Vignette nested in participants random intercept:

```{r}
# r.model.3 <- lmer(reason_vas ~ (1|vignette/id),
#                       data = final_long,
#                    
#                   na.action = "na.omit")
```

### Model 4

Vignette nested in participants which is then nested in labs:

```{r}
r.model.4 <- lmer(reason_vas ~ (1|vignette/person_code),
                      data = final_long,
                  na.action = "na.omit")
```

### Model 5

Addition of the covariates added to the vignette random intercept model. 

```{r}
r.model.5 <- lmer(reason_vas ~ (1|vignette/person_code) + 
                   comp + age + gender2 + education,
                      data = final_long,
                  na.action = "na.omit")
```
  
### Model 6

The previous model of covariates plus the variable of focus: condition.

```{r}
r.model.6 <- lmer(reason_vas ~ (1|vignette/person_code) + 
                   comp + age + gender2 + education + 
                   cond,
                      data = final_long,
                  na.action = "na.omit")
```

### Model 6A

Does the vignette interact with the condition?

```{r}
r.model.6A <- lmer(reason_vas ~ (1 | vignette/person_code) + 
                   comp + age + gender2 + education + 
                   cond*vignette,
                      data = final_long,
                  na.action = "na.omit")
```

### Model 6B

Data was collected from mechanical turk participants. Are there differences in this data and the complete data on the condition variable? 

```{r}
r.model.6B <- lmer(reason_vas ~ (1|vignette/person_code) + 
                    comp + age + gender2 + education + 
                    cond*turk,
                      data = final_long,
                  na.action = "na.omit")
```

## Final Analysis Luck

### Model 1 

Intercept only model to help determine if the addition of random intercepts are useful.

```{r}
l.model.1 <- glm(luck_vas ~ 1,
               data = final_luck,
                  na.action = "na.omit")
```

### Model 2

Vignette random intercept model:

```{r}
l.model.2 <- lmer(luck_vas ~ (1|vignette),
                      data = final_luck,
                  na.action = "na.omit")
```

### Model 3

Vignette nested in participants random intercept:

```{r}
# l.model.3 <- lmer(luck_vas ~ (1|vignette/id),
#                       data = final_luck,
#                   na.action = "na.omit")
```

### Model 4

Vignette nested in participants which is then nested in labs:

```{r}
l.model.4 <- lmer(luck_vas ~ (1|vignette/person_code),
                      data = final_luck,
                  na.action = "na.omit")
```
  
### Model 5

Addition of the covariates added to the vignette random intercept model. 

```{r}
l.model.5 <- lmer(luck_vas ~ (1|vignette/person_code) + 
                   comp + age + gender2 + education,
                      data = final_luck,
                  na.action = "na.omit")
```

### Model 6

The previous model of covariates plus the variable of focus: condition.

```{r}
l.model.6 <- lmer(luck_vas ~ (1|vignette/person_code) + 
                   comp + age + gender2 + education + 
                   cond,
                      data = final_luck,
                  na.action = "na.omit")
```

### Model 6A

Does the vignette interact with the condition?

```{r}
l.model.6A <- lmer(luck_vas ~ (1 | vignette/person_code) + 
                   comp + age + gender2 + education + 
                   cond*vignette,
                      data = final_luck,
                  na.action = "na.omit")
```

### Model 6B

Data was collected from mechanical turk participants. Are there differences in this data and the complete data on the condition variable? 

```{r}
l.model.6B <- lmer(luck_vas ~ (1|vignette/person_code) + 
                    comp + age + gender2 + education + 
                    cond*turk,
                      data = final_luck,
                  na.action = "na.omit")
```

## Write Out

```{r}
output <- list(
k.model.1, k.model.2, k.model.4, k.model.5, k.model.6, k.model.6A, k.model.6B, r.model.1, r.model.2, r.model.4, r.model.5, r.model.6, r.model.6A, r.model.6B, l.model.1, l.model.2, l.model.4, l.model.5, l.model.6, l.model.6A, l.model.6B)

save(output, file = "linear_noexclude.Rdata")
```


