---
title: "Analysis: Logistic with Updated Exclusions"
author: "erin buchanan"
date: "Last Updated `r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(scipen = 15)
```

## Update

Note: a good amount of code is eliminated to make this run faster. 

## Libraries

```{r}
library(rio)
library(lme4)
library(lmerTest)
library(nlme)
library(MuMIn)
library(plyr)
library(psych)
library(tidyr)
library(ggplot2)
library(dplyr)
library(ggmosaic)
library(MOTE)
library(flextable)
library(RColorBrewer)
```

## Load Data Clean Up

```{r}
load("clean_full_long.Rdata")
load("previousDF_wide.Rdata")
load("purposeDF_wide.Rdata")
```

## Study Exclusions

In this section, we will mark each exclusion criteria to be able to denote how many exclusions each participant may have had.

### Majority Age

(1) if the participant is not the majority age of their country or older (unless parent/guardian waiver provided)

In this section, we will exclude all participants who are under 18 or are not the majority age of their country or older.

https://en.wikipedia.org/wiki/Age_of_majority

```{r}
# table of lab countries
full_long$lab_country <- droplevels(full_long$lab_country)
table(full_long$lab_country, useNA = "ifany")

# age information
summary(full_long$age)

# minimum age by country
tapply(full_long$age, full_long$lab_country, min, na.rm = T)

# exclude based on age
full_long$age_exclusion <- NA

# everyone under 18
full_long$age_exclusion <- full_long$age < 18

# everyone over 100 
full_long$age_exclusion[full_long$age > 100] <- TRUE

# TWN age of majority is 20 at time of study
full_long$age_exclusion[full_long$lab_country %in% "TWN"] <- full_long$age[full_long$lab_country %in% "TWN"] < 20
```

### Previous Knowledge/Participation of Study 

(2) if the participant has taken part in a previous version of this study or in another contributors' replication of the same study

```{r}
full_long <- merge(full_long,
                   previousDF_wide[ , c("id", "exclude", "nonsense")], all.x = T) 

# number of rows
nrow(full_long)
# number of participants
length(unique(full_long$id))

colnames(full_long)[(ncol(full_long)-1):ncol(full_long)] <- c("previous_exclusion", "previous_nonsense")

full_long$previous_exclusion[full_long$previous == ""] <- FALSE
full_long$previous_nonsense[full_long$previous == ""] <- FALSE
full_long$previous_exclusion[is.na(full_long$previous)] <- FALSE
full_long$previous_nonsense[is.na(full_long$previous)] <- FALSE
full_long$previous_exclusion[nchar(full_long$previous) < 2] <- FALSE
full_long$previous_nonsense[nchar(full_long$previous) < 2] <- FALSE
```

### Comprehension Questions 

(3) if the participant fails to answer comprehension questions correctly

```{r}
table(full_long$dge_valid)

full_long$studyans_exclusion <- !(full_long$dge_valid)

table(full_long$compr, full_long$vignette)
```

### Knowledge of Experiment/Hypothesis 

(4) if the participant correctly and explicitly articulate knowledge of the specific hypotheses or specific conditions of this study when answering the funneled debriefing questions. 

```{r}
full_long <- merge(full_long,
                   purposeDF_wide[ , c("id", "exclude", "nonsense")], all.x = T) 

# number of rows
nrow(full_long)
# number of participants
length(unique(full_long$id))

colnames(full_long)[(ncol(full_long)-1):ncol(full_long)] <- c("purpose_exclusion", "purpose_nonsense")

full_long$purpose_exclusion[full_long$purpose == ""] <- FALSE
full_long$purpose_nonsense[full_long$purpose == ""] <- FALSE
full_long$purpose_exclusion[is.na(full_long$purpose)] <- FALSE
full_long$purpose_nonsense[is.na(full_long$purpose)] <- FALSE
full_long$purpose_exclusion[nchar(full_long$purpose) < 2] <- FALSE
full_long$purpose_nonsense[nchar(full_long$purpose) < 2] <- FALSE 

# missing_purpose <-
#   full_long %>%
#        filter(is.na(purpose_exclusion)) %>%
#        select(purpose, id, survey_lang) %>%
#        unique()
# write.csv(missing_purpose, "../04_Data/data/aus_update_purpose.csv", row.names = F)
# 
# missing_previous <-
#     full_long %>%
#        filter(is.na(previous_exclusion)) %>%
#        select(previous, id, survey_lang) %>%
#        unique()
# write.csv(missing_previous, "../04_Data/data/aus_update_previous.csv", row.names = F)
```

### Language Proficiency 

We will also exclude participants who self-report their understanding of the tested language as "not well" or "not well at all". We based this exclusion criteria on a recent study that found that non-native English speakers who self-report as "very well" and "well" tend to score in the "intermediate" and "basic" categories on an English proficiency test respectively, while those who self-report as "not well" and "not at all" tend to score in the "below basic" category (Vickstrom, Shin, Collazo, & Bauman, 2015). All excluded data will be included in the data files on the overall OSF page, along with the particular reason for why they were excluded. 

```{r}
summary(full_long$language)

full_long$lang_exclusion <- full_long$language == "not very well" | full_long$language == "not well at all" 
```

### Total Exclusions

In this section, we provide the total (data point) exclusions for each particular screening item plus a table with all exclusions forever. 

```{r}
# exclusions individually
table(full_long$age_exclusion, useNA = "ifany") / 3
table(full_long$lang_exclusion, useNA = "ifany") / 3
table(full_long$studyans_exclusion, useNA = "ifany") / 3
table(full_long$previous_exclusion, useNA = "ifany") / 3
table(full_long$purpose_exclusion, useNA = "ifany") / 3 

# for these, NA means they should be excluded
full_long$age_exclusion[is.na(full_long$age_exclusion)] <- TRUE
full_long$lang_exclusion[is.na(full_long$lang_exclusion)] <- TRUE
full_long$studyans_exclusion[is.na(full_long$studyans_exclusion)] <- TRUE

# for these, NA means no answer which is ok 
full_long$previous_exclusion[is.na(full_long$previous_exclusion)] <- FALSE
full_long$purpose_exclusion[is.na(full_long$purpose_exclusion)] <- FALSE

full_long$total_exclusion <- apply(full_long[ , grep("exclusion", colnames(full_long))], 1, sum, na.rm = T)

table(full_long$total_exclusion, useNA = "ifany") / 3

# multiway table of all exclusions 
exclusions <- as.data.frame(table(full_long$age_exclusion, 
                                  full_long$lang_exclusion, 
                                  full_long$previous_exclusion,
                                  full_long$purpose_exclusion, 
                                  full_long$studyans_exclusion, useNA = "ifany"))
colnames(exclusions) <- c("Age", "Language", "Previous", "Purpose", "Comprehension", "Frequency")
exclusions$Num_Participants <- exclusions$Frequency / 3

exclusions

final_long <- subset(full_long, total_exclusion < 1)

# drop all the levels that no longer exist within the data 
final_long <- droplevels(final_long)

# total number data points originally
nrow(full_long) 
# total number data points now
nrow(final_long) 

# original number of participants 
length(unique(full_long$id)) 
# final number of participants 
length(unique(final_long$id)) 
```

## Code We Need

```{r}
final_long$bin_order <- droplevels(final_long$bin_order)

# drop levels
final_long$id <- factor(final_long$id)
final_long$vignette <- factor(final_long$vignette)

# for luck analyses people should be excluded if they get the answer wrong 
final_long$luck_correct <- FALSE

final_long$ri_wr <- factor(final_long$ri_wr, 
                           levels = c(1,2),
                           labels = c("Right", "Wrong"))
final_long$luck_correct[final_long$cond == "Ignorance" & final_long$ri_wr == "Wrong"] <- TRUE
final_long$luck_correct[final_long$cond != "Ignorance" & final_long$ri_wr == "Right"] <- TRUE

# subset the wrong answers 
final_luck <- subset(final_long, luck_correct)

final_long$bin_order <- droplevels(final_long$bin_order)
```

### Update DV  

In this instance, we do not see any form of linearity or homoscedasticity - the data is clearly skewed or bimodal. Therefore, we decided to split the VAS scale into 40 and below and 60 and above, then combine with the truly binary data, and include this variable to understand if there were differences when the VAS scale did not produce continuous data. 

Please note that the VAS is scored in the opposite direction of the BIN scales, therefore, you will see that the data split corrects this directionality difference. 

```{r}
## knowledge
table(final_long$know_bin, useNA = "ifany")

## split data 
final_long$know_vas_binned <- final_long$know_vas
final_long$know_vas_binned[final_long$know_vas_binned <= 40] <- 2
final_long$know_vas_binned[final_long$know_vas_binned > 40 & 
                             final_long$know_vas_binned < 60] <- NA
final_long$know_vas_binned[final_long$know_vas_binned >= 60] <- 1
table(final_long$know_vas_binned, useNA = "ifany")

# no overlap
table(final_long$know_bin, final_long$know_vas_binned, useNA = "ifany")

final_long$know_vas_combined <- ifelse(is.na(final_long$know_vas_binned), 
                                     final_long$know_bin, 
                                     final_long$know_vas_binned)

final_long$know_vas_combined_source <- ifelse(is.na(final_long$know_vas_binned), 
                                     "Binary", 
                                     "VAS")

table(final_long$know_vas_combined, useNA = "ifany")
table(final_long$know_vas_combined_source, useNA = "ifany")

## reasonable
table(final_long$reason_bin, useNA = "ifany")

## split data 
final_long$reason_vas_binned <- final_long$reason_vas
final_long$reason_vas_binned[final_long$reason_vas_binned <= 40] <- 2
final_long$reason_vas_binned[final_long$reason_vas_binned > 40 & 
                             final_long$reason_vas_binned < 60] <- NA
final_long$reason_vas_binned[final_long$reason_vas_binned >= 60] <- 1
table(final_long$reason_vas_binned, useNA = "ifany")

# no overlap
table(final_long$reason_bin, final_long$reason_vas_binned, useNA = "ifany")

final_long$reason_vas_combined <- ifelse(is.na(final_long$reason_vas_binned), 
                                     final_long$reason_bin, 
                                     final_long$reason_vas_binned)

final_long$reason_vas_combined_source <- ifelse(is.na(final_long$reason_vas_binned), 
                                     "Binary", 
                                     "VAS")

table(final_long$reason_vas_combined, useNA = "ifany")
table(final_long$reason_vas_combined_source, useNA = "ifany")

## luck
table(final_luck$luck_bin, useNA = "ifany")

## split data 
final_luck$luck_vas_binned <- final_luck$luck_vas
final_luck$luck_vas_binned[final_luck$luck_vas_binned <= 40] <- 2
final_luck$luck_vas_binned[final_luck$luck_vas_binned > 40 & 
                             final_luck$luck_vas_binned < 60] <- NA
final_luck$luck_vas_binned[final_luck$luck_vas_binned >= 60] <- 1
table(final_luck$luck_vas_binned, useNA = "ifany")

# no overlap
table(final_luck$luck_bin, final_luck$luck_vas_binned, useNA = "ifany")

final_luck$luck_vas_combined <- ifelse(is.na(final_luck$luck_vas_binned), 
                                     final_luck$luck_bin, 
                                     final_luck$luck_vas_binned)

final_luck$luck_vas_combined_source <- ifelse(is.na(final_luck$luck_vas_binned), 
                                     "Binary", 
                                     "VAS")

table(final_luck$luck_vas_combined, useNA = "ifany")
table(final_luck$luck_vas_combined_source, useNA = "ifany")
```

We recoded knowledge and reasonableness for easier processing in the paper.

```{r}
table(final_long$know_vas_combined)
final_long$know_vas_combined <- 3 - final_long$know_vas_combined 
table(final_long$know_vas_combined)

table(final_long$reason_vas_combined)
final_long$reason_vas_combined <- 3 - final_long$reason_vas_combined 
table(final_long$reason_vas_combined)
```

### Gender Other

Because of the small other category, we will simply compare male to female. 

```{r}
final_long$gender2 <- factor(final_long$gender,
                             levels = c("female", "male"))

final_luck$gender2 <- factor(final_luck$gender,
                             levels = c("female", "male"))

table(final_long$gender, useNA = "ifany")
table(final_long$gender2, useNA = "ifany")
```

## Final Analysis Knowledge

### Model 1 

Intercept only model to help determine if the addition of random intercepts are useful.

```{r}
#scores should be 0 and 1 for this analysis 
final_long$know_vas_combined <- final_long$know_vas_combined - 1

k.model.1 <- glm(know_vas_combined ~ 1,
               data = final_long,
               family = binomial,
               na.action = "na.omit")
```

### Model 2

Vignette random intercept model:

```{r}
k.model.2 <- glmer(know_vas_combined ~ (1|vignette),
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 3

Vignette nested in participants random intercept:

```{r}
k.model.3 <- glmer(know_vas_combined ~ (1|vignette/id),
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```
  
### Model 4

Vignette nested in participants which is then nested in labs:

```{r}
k.model.4 <- glmer(know_vas_combined ~ (1|vignette/id/person_code),
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```
  
### Model 5

Addition of the covariates added to the vignette random intercept model. 

```{r}
k.model.5 <- glmer(know_vas_combined ~ (1|vignette/id/person_code) + 
                   comp + age + gender2 + education,
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```
  
### Model 6

The previous model of covariates plus the variable of focus: condition.

```{r}
k.model.6 <- glmer(know_vas_combined ~ (1|vignette/id/person_code) + 
                   comp + age + gender2 + education + 
                   cond,
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 6A

Does the vignette interact with the condition?

```{r}
k.model.6A <- glmer(know_vas_combined ~ (1 | vignette/id/person_code) + 
                   comp + age + gender2 + education + 
                   cond*vignette,
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

```{r}
data_graph <- k.model.6A@frame
data_graph$know_vas_combined <- factor(data_graph$know_vas_combined,
                                          levels = c(0,1),
                                          labels = c("Believes", "Knows"))

# overall darrel
k.d_table <- table(data_graph$know_vas_combined[data_graph$vignette == "Darrel"], 
           data_graph$cond[data_graph$vignette == "Darrel"])

# overall emma
k.e_table <- table(data_graph$know_vas_combined[data_graph$vignette == "Emma"], 
           data_graph$cond[data_graph$vignette == "Emma"])

# overall gerald
k.g_table <- table(data_graph$know_vas_combined[data_graph$vignette == "Gerald"], 
           data_graph$cond[data_graph$vignette == "Gerald"])
```

### Model 6B

Data was collected from mechanical turk participants. Are there differences in this data and the complete data on the condition variable? 

```{r}
k.model.6B <- glmer(know_vas_combined ~ (1|vignette/id/person_code) + 
                    comp + age + gender2 + education + 
                    cond*turk,
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```
  
## Final Analysis Reasonableness

### Model 1 

Intercept only model to help determine if the addition of random intercepts are useful.

```{r}
#scores should be 0 and 1 for this analysis 
final_long$reason_vas_combined <- final_long$reason_vas_combined - 1

r.model.1 <- glm(reason_vas_combined ~ 1,
               data = final_long,
               family = binomial,
               na.action = "na.omit")
```

### Model 2

Vignette random intercept model:

```{r}
r.model.2 <- glmer(reason_vas_combined ~ (1|vignette),
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```
  
### Model 3

Vignette nested in participants random intercept:

```{r}
r.model.3 <- glmer(reason_vas_combined ~ (1|vignette/id),
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 4

Vignette nested in participants which is then nested in labs:

```{r}
r.model.4 <- glmer(reason_vas_combined ~ (1|vignette/id/person_code),
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 5

Addition of the covariates added to the vignette random intercept model. 

```{r}
r.model.5 <- glmer(reason_vas_combined ~ (1|vignette/id/person_code) + 
                   comp + age + gender2 + education,
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```
  
### Model 6

The previous model of covariates plus the variable of focus: condition.

```{r}
r.model.6 <- glmer(reason_vas_combined ~ (1|vignette/id/person_code) + 
                   comp + age + gender2 + education + 
                   cond,
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 6A

Does the vignette interact with the condition?

```{r}
r.model.6A <- glmer(reason_vas_combined ~ (1 | vignette/id/person_code) + 
                   comp + age + gender2 + education + 
                   cond*vignette,
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

```{r}
r.data_graph <- r.model.6A@frame
r.data_graph$reason_vas_combined <- factor(r.data_graph$reason_vas_combined,
                                          levels = c(0,1),
                                          labels = c("Unreasonable", "Reasonable"))

# overall darrel
r.d_table <- table(r.data_graph$reason_vas_combined[r.data_graph$vignette == "Darrel"], 
           r.data_graph$cond[r.data_graph$vignette == "Darrel"])

# overall emma
r.e_table <- table(r.data_graph$reason_vas_combined[r.data_graph$vignette == "Emma"], 
           r.data_graph$cond[r.data_graph$vignette == "Emma"])

# overall gerald
r.g_table <- table(r.data_graph$reason_vas_combined[r.data_graph$vignette == "Gerald"], 
           r.data_graph$cond[r.data_graph$vignette == "Gerald"])
```

### Model 6B

Data was collected from mechanical turk participants. Are there differences in this data and the complete data on the condition variable? 

```{r}
r.model.6B <- glmer(reason_vas_combined ~ (1|vignette/id/person_code) + 
                    comp + age + gender2 + education + 
                    cond*turk,
                      data = final_long,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

## Final Analysis Luck

### Model 1 

Intercept only model to help determine if the addition of random intercepts are useful.

```{r}
#scores should be 0 and 1 for this analysis 
final_luck$luck_vas_combined <- final_luck$luck_vas_combined - 1

l.model.1 <- glm(luck_vas_combined ~ 1,
               data = final_luck,
               family = binomial,
               na.action = "na.omit")
```

### Model 2

Vignette random intercept model:

```{r}
l.model.2 <- glmer(luck_vas_combined ~ (1|vignette),
                      data = final_luck,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 3

Vignette nested in participants random intercept:

```{r}
l.model.3 <- glmer(luck_vas_combined ~ (1|vignette/id),
                      data = final_luck,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 4

Vignette nested in participants which is then nested in labs:

```{r}
l.model.4 <- glmer(luck_vas_combined ~ (1|vignette/id/person_code),
                      data = final_luck,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```
  
### Model 5

Addition of the covariates added to the vignette random intercept model. 

```{r}
l.model.5 <- glmer(luck_vas_combined ~ (1|vignette/id/person_code) + 
                   comp + age + gender2 + education,
                      data = final_luck,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 6

The previous model of covariates plus the variable of focus: condition.

```{r}
l.model.6 <- glmer(luck_vas_combined ~ (1|vignette/id/person_code) + 
                   comp + age + gender2 + education + 
                   cond,
                      data = final_luck,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

### Model 6A

Does the vignette interact with the condition?

```{r}
l.model.6A <- glmer(luck_vas_combined ~ (1 | vignette/id/person_code) + 
                   comp + age + gender2 + education + 
                   cond*vignette,
                      data = final_luck,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

```{r}
l.data_graph <- l.model.6A@frame
l.data_graph$luck_vas_combined <- factor(l.data_graph$luck_vas_combined,
                                          levels = c(0,1),
                                          labels = c("Luck", "Ability"))

# overall darrel
l.d_table <- table(l.data_graph$luck_vas_combined[l.data_graph$vignette == "Darrel"], 
           l.data_graph$cond[l.data_graph$vignette == "Darrel"])

# overall emma
l.e_table <- table(l.data_graph$luck_vas_combined[l.data_graph$vignette == "Emma"], 
           l.data_graph$cond[l.data_graph$vignette == "Emma"])

# overall gerald
l.g_table <- table(l.data_graph$luck_vas_combined[l.data_graph$vignette == "Gerald"], 
           l.data_graph$cond[l.data_graph$vignette == "Gerald"])
```

### Model 6B

Data was collected from mechanical turk participants. Are there differences in this data and the complete data on the condition variable? 

```{r}
l.model.6B <- glmer(luck_vas_combined ~ (1|vignette/id/person_code) + 
                    comp + age + gender2 + education + 
                    cond*turk,
                      data = final_luck,
                      family = binomial,
                      control = glmerControl(optimizer = "bobyqa"),
                      nAGQ = 0)
```

## Write Out

```{r}
output <- list(
k.model.1, k.model.2, k.model.3, k.model.4, k.model.5, k.model.6, k.model.6A, k.model.6B, r.model.1, r.model.2, r.model.3, r.model.4, r.model.5, r.model.6, r.model.6A, r.model.6B, l.model.1, l.model.2, l.model.3, l.model.4, l.model.5, l.model.6, l.model.6A, r.model.6B)

save(output, file = "log_exclude.Rdata")
save(full_long, file = "full_long_log_exclude.Rdata")
save(final_long, file = "final_long_log_exclude.Rdata")
save(final_luck, file = "final_luck_log_exclude.Rdata")
```


