---
title: "Author_List"
author: "erin buchanan"
date: "Last Knitted: `r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#libraries
library(gsheet)
library(rio)
library(flextable)
library(dplyr)
set.seed(89088934)
```

```{r}
#grab tenzing information
lab_gsheet <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1A_GoD3y6t0FTdrVCUPHlXorZxLxeEC-o2B3Ieg5wqcc/edit?usp=sharing")

colnames(lab_gsheet) <- c("tier", "first", "middle", "last", "full_name", 
                          "b_check", "s_check", "j_check", 
                          "conceptualization", "data_curation", "analysis", 
                          "funding", "investigation", "methodology", "p_admin", 
                          "resources", "translation", "software", "supervision",
                           "validation",  "visualization", "writing_original", 
                          "writing_review", "credit_count", "email", "email_nouse", "email_check",
                          "affiliation", "second_aff", "PSA_ID", 
                          "ammps_account", "author_stage1", "author_stage2", 
                          "data_check", "community_check", "funding_check", "orcid", 
                          "corresponding")

#grab author survey
author <- import("author_survey.csv")

#clean up author survey
colnames(author) <- c("name", "id", "PSA_ID", "section", "section_id", "section_sis_id",
                      "submitted", "attempt", "overview", "score1", "full_name", 
                      "score2", "citation_name", "score3", "email", "score4", 
                      "students", "score5", "ammps_note", "score6", "credit", 
                      "score7", "credit_write", "score8", "institution", 
                      "score9", "department", "score10", "country", "score11",
                      "cois", "score12", "ammps_check", "score13", "data", "score14", 
                      "community", "score15", "inperson", "score16", "individual", 
                      "score17", "recruitment", "score18", "compensation", 
                      "score19", "datacollect", "score20", "qualtrics", "score21", 
                      "extensions", "score22", "covid", "score23", "funding_report",
                      "score24", "old1", "old2", "old3", "old4", "score25", "score26", 
                      "total_score")

author <- author[ , !grepl("old|^score|section", colnames(author))]

#sort by date and eliminate duplicates
author <- author[order(author$submitted, decreasing = T) , ]
author <- author[!duplicated(author$PSA_ID), ]
author$PSA_ID <- as.character(author$PSA_ID)

#merge with main data 
alldata <- lab_gsheet %>% 
  full_join(author, by = c("PSA_ID" = "PSA_ID"))

# add in admin team since some of us can't take the survey
# just make sure these people mark the google sheet as the right info
admin_id <- c("1729", "139", "47", "22", "1817", "1751", "14", "175")
alldata$attempt[alldata$PSA_ID %in% admin_id] <- 1 
```

## Fill in Missing PSA_IDs

```{r}
# check for blank PSA_IDs
flextable(
  alldata %>% filter(is.na(PSA_ID) | PSA_ID == "None") %>% 
  select(full_name.x, email.x, email.y)
) %>% autofit() %>% fit_to_width(7.5)
```

## Check for Duplicated IDs 

```{r}
# make sure not duplicated PSAID
# remember that NAs are considered duplicates 
if (sum(duplicated(alldata$PSA_ID)) > 0){
  alldata$full_name.x[duplicated(alldata$PSA_ID)]
  
  alldata$PSA_ID[duplicated(alldata$PSA_ID)]
}
```

## Find Missing People

```{r}
alldata %>% filter(is.na(first)) %>% select(PSA_ID, full_name.y)

alldata <- 
  alldata %>% 
  filter(PSA_ID != "272") %>%  #asked to be removed
  filter(PSA_ID != "513")  #asked to be removed 
```

## Fix Names

```{r}
# check what they wrote in canvas versus what we have 
flextable(
  alldata %>% filter(full_name.x != full_name.y) %>% select(full_name.x, full_name.y, PSA_ID)
) %>% autofit() %>% fit_to_width(7.5)

# check what we have in canvas matches the name in our worksheet
flextable(
  alldata %>% filter(full_name.x != name) %>% select(full_name.x, name, PSA_ID)
) %>% autofit() %>% fit_to_width(7.5)
```

## Fix Emails

```{r}
# check what they said in canvas versus what we have 
flextable(
  alldata %>% filter(email.x != email.y) %>% select(email.x, email.y, PSA_ID)
) %>% autofit() %>% fit_to_width(7.5)
```

## Order

```{r}
alldata$credit_total <- apply(alldata %>% 
                                select(conceptualization, data_curation,
                                       analysis, funding, investigation,
                                       methodology, p_admin, resources, 
                                       software, supervision, 
                                       validation, visualization, 
                                       writing_original, writing_review), 1, sum)

author_order <- c(
  #first Hall, Schmidt, Wagge, Lewis, Weissgerber, Kiunke
  "1729", "139", "47", "22", "1817", "1751", 
  # 3+ credit and community
  alldata %>% filter(credit_total > 2) %>% filter(community == "Yes") %>% arrange(desc(credit_total), last) %>% pull(PSA_ID), 
  # 3+ credit
  alldata %>% filter(credit_total > 2) %>% arrange(desc(credit_total), last) %>%  pull(PSA_ID), 
  # 2 credit and community
  alldata %>% filter(credit_total == 2) %>% filter(community == "Yes")  %>% arrange(last) %>% pull(PSA_ID), 
  # 2 credit 
  alldata %>% filter(credit_total == 2) %>% arrange(last) %>% pull(PSA_ID)
)

# remove duplicates and NAs
author_order <- na.omit(author_order)
author_order <- author_order[author_order != "None"]
author_order <- author_order[!duplicated(author_order)]
author_order <- c(author_order[!(author_order %in% c("14", "175"))], "175", "14") # Buchanan, Moshontz 
```

## Authorship

```{r}
# fill in admin "survey"
# we are using email and name from our curated sheet
# then department institution country from the survey
alldata$department[alldata$PSA_ID %in% admin_id] <- 
  c("Analytics", "Psychology", "Psychology", "Psychology", 
    "Psychology", "Psychology", "Psychology", "Psychology")

alldata$institution[alldata$PSA_ID %in% admin_id] <- 
  c("Harrisburg University of Science and Technology", 
    "Ashland University", 
    "University of Kassel", 
    "Ashland University", 
    "University of Wisconsin-Madison", 
    "Southern Illinois University Carbondale", 
    "Avila University", 
    "University of Kassel")

alldata$country[alldata$PSA_ID %in% admin_id] <- 
  c("USA", "USA", "Germany", "USA", "USA", "USA", "USA", "Germany")
```

```{r}
# print out authorship 
ordered_author <- 
  alldata %>% 
  filter(PSA_ID %in% author_order) %>% 
  arrange(match(PSA_ID, author_order)) %>% 
  mutate(full_survey = paste(full_name.x, department, institution, country, email.x, sep = ", "), 
         full_ours = paste(full_name.x, affiliation, email.x, sep = ", "))

# just check this to make sure you shouldn't exclude
ordered_author %>% filter(total_score < 10)

ordered_author <- ordered_author %>% 
  filter(!is.na(attempt))
```

### Final People Who Did the Survey

`r paste(ordered_author$full_survey[!is.na(ordered_author$attempt)], collapse = "  \n\n")`

### Create Upload CSV 

## Credit

```{r}
ordered_author <- 
  ordered_author %>% mutate(credit_name = paste(substr(full_name.x, 1, 1), ". ", 
                                         middle, " ", last, sep = "")) %>% 
  mutate(credit_name = gsub("NA", "", credit_name)) %>% 
  mutate(credit_name = gsub("  ", " ", credit_name)) 
```
  
`r paste(ordered_author %>% filter(conceptualization) %>% pull(credit_name), collapse = ", ")` contributed to the conceptualization of the project. 

`r paste(ordered_author %>% filter(writing_original) %>% pull(credit_name), collapse = ", ")` wrote the original draft of this report.

`r paste(ordered_author %>% filter(writing_review) %>% pull(credit_name), collapse = ", ")` edited, reviewed, and revised the draft of this report.

`r paste(ordered_author %>% filter(data_curation) %>% pull(credit_name), collapse = ", ")` contributed to the data curation.

`r paste(ordered_author %>% filter(analysis) %>% pull(credit_name), collapse = ", ")` contributed to the analysis of the data.

`r paste(ordered_author %>% filter(funding) %>% pull(credit_name), collapse = ", ")` secured funding for this project. 

`r paste(ordered_author %>% filter(supervision) %>% pull(credit_name), collapse = ", ")` was invovled in supervision for this project including supervision of student led teams.

`r paste(ordered_author %>% filter(investigation) %>% pull(credit_name), collapse = ", ")` contributed to the data collection and investigation. 

`r paste(ordered_author %>% filter(methodology) %>% pull(credit_name), collapse = ", ")` contributed to methodology for the project.

`r paste(ordered_author %>% filter(resources) %>% pull(credit_name), collapse = ", ")` contributed to resources for this project.

`r paste(ordered_author %>% filter(translation) %>% pull(credit_name), collapse = ", ")` contributed to the translation for materials for this project. 

`r paste(ordered_author %>% filter(software) %>% pull(credit_name), collapse = ", ")` contributed survey software and coding for this project.

`r paste(ordered_author %>% filter(validation) %>% pull(credit_name), collapse = ", ")` contributed validation of the analyses. 

`r paste(ordered_author %>% filter(visualization) %>% pull(credit_name), collapse = ", ")` contributed to the visualization of data and analyses. 

## COIs

```{r}
flextable(ordered_author %>% select(PSA_ID, full_name.x, cois)) %>% autofit() %>% fit_to_width(7.5)
```

## Funding 

```{r}
#table(ordered_author$funding_report)
ordered_author$funding_report2 <- gsub("-|I do not have.*|N.A.*|n\\/a.*|N\\/A.*|^NA|^na|^NO|^No|^no", NA, ordered_author$funding_report)
ordered_author$funding_report2[ordered_author$funding_report2 == ""] <- NA

ordered_author$funding_report2[!is.na(ordered_author$funding_report2)] <- paste(ordered_author$full_name.x[!is.na(ordered_author$funding_report2)], ": ", ordered_author$funding_report2[!is.na(ordered_author$funding_report2)], sep = "")

# # move simona
simona <- as.numeric(rownames(ordered_author)[ordered_author$last == "Ďurbisová"])
ordered_author <- ordered_author[c(1:35,  simona, 36:(simona-1), (simona+1):length(ordered_author$first)) , ]
```

`r paste(na.omit(ordered_author$funding_report2), collapse = "  \n\n")`

## Acknowledgement List 

```{r}
#View(ordered_author %>% select(first, last, affiliation, second_aff))

library(tenzing)

# validate_contributors_table(contributors_table = ordered_author)

ordered_tenzing <- ordered_author %>% 
  mutate(`Order in publication` = 1:nrow(ordered_author)) %>% 
  select(`Order in publication`, first, middle, last, conceptualization:writing_review, email.x, 
         affiliation, second_aff, funding_report, orcid, corresponding) %>% 
  select(-translation)

colnames(ordered_tenzing) <- 
  c("Order in publication", "Firstname", "Middle name", "Surname",
    "Conceptualization", "Data curation", "Formal analysis", 
    "Funding acquisition", "Investigation", "Methodology",
    "Project administration", "Resources", "Software",  
    "Supervision",   "Validation", "Visualization",
    "Writing - original draft", "Writing - review & editing", 
    "Email address", "Primary affiliation", "Secondary affiliation", "Funding", "ORCID iD",  "Corresponding author?")

#validate_contributors_table(contributors_table = ordered_tenzing)

cat(print_yaml(contributors_table = ordered_tenzing))

cat(print_funding(contributors_table = ordered_tenzing))
```

