---
title: "Author_List"
author: "erin buchanan"
date: "Last Knitted: `r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
#libraries
library(gsheet)
library(rio)
library(flextable)
library(dplyr)
set.seed(89088934)
```

```{r}
#grab tenzing information
lab_gsheet <- gsheet2tbl("https://docs.google.com/spreadsheets/d/1A_GoD3y6t0FTdrVCUPHlXorZxLxeEC-o2B3Ieg5wqcc/edit?usp=sharing")

colnames(lab_gsheet) <- c("tier", "first", "middle", "last", "full_name", 
                          "b_check", "s_check", "j_check", "p_admin", 
                          "conceptualization", "writing_original", 
                          "writing_review", "data_curation", "analysis", 
                          "funding", "supervision", "investigation", "methodology", 
                          "resources", "translation", "software", "validation", 
                          "visualization", "email", "email_nouse", "email_check",
                          "affiliation", "PSA_ID", 
                          "ammps_account", "author_stage1", "author_stage2", 
                          "data_check", "community_check", "funding_check", "orcid", 
                          "corresponding")

#grab author survey
author <- import("author_survey.csv")

#clean up author survey
colnames(author) <- c("name", "id", "PSA_ID", "section", "section_id", "section_sis_id",
                      "submitted", "attempt", "overview", "score1", "full_name", 
                      "score2", "citation_name", "score3", "email", "score4", 
                      "students", "score5", "ammps_note", "score6", "credit", 
                      "score7", "credit_write", "score8", "institution", 
                      "score9", "department", "score10", "country", "score11",
                      "cois", "score12", "ammps_check", "score13", "data", "score14", 
                      "community", "score15", "inperson", "score16", "individual", 
                      "score17", "recruitment", "score18", "compensation", 
                      "score19", "datacollect", "score20", "qualtrics", "score21", 
                      "extensions", "score22", "covid", "score23", "funding_report",
                      "score24", paste("old", 1:34, sep = ""), "total_score")


author <- author[ , !grepl("old|^score|section", colnames(author))]

#sort by date and eliminate duplicates
author <- author[order(author$submitted, decreasing = T) , ]
author <- author[!duplicated(author$PSA_ID), ]
author$PSA_ID <- as.character(author$PSA_ID)

#merge with main data 
alldata <- lab_gsheet %>% 
  full_join(author, by = c("PSA_ID" = "PSA_ID"))

# add in admin team since some of us can't take the survey
# just make sure these people mark the google sheet as the right info
admin_id <- c("1729", "139", "47", "22", "1817", "1751", "14", "175")
alldata$attempt[alldata$PSA_ID %in% admin_id] <- 1 
```

## Fill in Missing PSA_IDs

```{r}
# check for blank PSA_IDs
alldata$full_name.x[is.na(alldata$PSA_ID)]
```

## Check for Duplicated IDs 

```{r}
# make sure not duplicated PSAID
# remember that NAs are considered duplicates 
if (sum(duplicated(alldata$PSA_ID)) > 0){
  alldata$full_name.x[duplicated(alldata$PSA_ID)]
}
```

## Fix Names

```{r}
flextable(
  alldata %>% filter(full_name.x != full_name.y) %>% select(full_name.x, full_name.y, PSA_ID)
)
```

## Fix Emails

```{r}
flextable(
  alldata %>% filter(email.x != email.y) %>% select(email.x, email.y, PSA_ID)
)
```

## Order

```{r}
alldata$credit_total <- apply(alldata %>% select(p_admin, conceptualization, 
                                               writing_original, writing_review,
                                               data_curation, analysis, 
                                               funding, supervision, 
                                               investigation, methodology, 
                                               resources, translation, 
                                               software, validation, 
                                               visualization), 1, sum, na.omit = T)

author_order <- c(
  #first Hall, Schmidt, Wagge, Lewis, Weissgerber, Kiunke
  "1729", "139", "47", "22", "1817", "1751", 
  # 3+ credit and community
  alldata %>% filter(credit_total > 2) %>% filter(community == "Yes") %>% arrange(desc(credit_total)) %>% pull(PSA_ID), 
  # 3+ credit
  alldata %>% filter(credit_total > 2) %>% arrange(desc(credit_total)) %>%  pull(PSA_ID), 
  # 2 credit and community
  alldata %>% filter(credit_total > 1) %>% filter(community == "Yes") %>% pull(PSA_ID), 
  # 2 credit 
  alldata %>% filter(credit_total > 1) %>% pull(PSA_ID)
)

# remove duplicates and NAs
author_order <- na.omit(author_order)
author_order <- author_order[!duplicated(author_order)]
author_order <- c(author_order[!(author_order %in% c("14", "175"))], "14", "175") # Buchanan, Moshontz 
```

## Authorship

```{r}
# fill in admin "survey"
# we are using email and name from our curated sheet
# then department institution country from the survey
alldata$department[alldata$PSA_ID %in% admin_id] <- 
  c("Analytics", "Psychology", "Psychology", "Psychology", 
    "Psychology", "Psychology", "Psychology", "Psychology")

alldata$institution[alldata$PSA_ID %in% admin_id] <- 
  c("Harrisburg University of Science and Technology", 
    "Southern Illinois University Carbondale", 
    "Universität Kassel", 
    "Ashland University", 
    "University of Wisconsin-Madison", 
    "Southern Illinois University Carbondale", 
    "Avila University", 
    "Universität Kassel")


alldata$country[alldata$PSA_ID %in% admin_id] <- 
  c("USA", "USA", "Germany", "USA", "USA", "USA", "USA", "Germany")
```


```{r}
# print out authorship 
ordered_author <- 
  alldata %>% 
  filter(PSA_ID %in% author_order) %>% 
  arrange(match(PSA_ID, author_order)) %>% 
  mutate(full_survey = paste(full_name.x, department, institution, country, email.x, sep = ", "), 
         full_ours = paste(full_name.x, affiliation, email.x, sep = ", "))

# just check this to make sure you shouldn't exclude
ordered_author %>% filter(total_score == 0)
```

### Using Survey

`r paste(ordered_author$full_survey, collapse = "  \n")`

### Using Our Data

`r paste(ordered_author$full_ours, collapse = "  \n")`

### Final People Who Did the Survey

`r paste(ordered_author$full_survey[!is.na(ordered_author$attempt)], collapse = "  \n")`

### Create Upload CSV 

## Credit

## COIs

```{r}
flextable(ordered_author %>% select(PSA_ID, full_name.x, cois))
```


## Funding 

```{r}
flextable(ordered_author %>% select(PSA_ID, full_name.x, funding_report))
```

## Acknowledgement List 
