---
title: "CREP - PSA004 Log"
date: "Last Updated: `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

```{r echo = F, message = F}
#devtools::install_github("joon-e/soscisurvey")
#https://github.com/joon-e/soscisurvey

library(soscisurvey)
library(purrr)
library(flextable)
library(tidyr)

df <- read_sosci("https://www.soscisurvey.de/AccCREP_RRR_rev_f/?act=nC3iqEvRkDO5HJyTJhPJCm41")
df <- purrr::modify(df, labelled::user_na_to_na)
all_rows <- as.data.frame(table(toupper(df$lab_ID)))
df <- subset(df, !is.na(Name_order))
#purrr::modify_if(data, ~ attr(., "var.type") %in% c("nominal", "dichotomous"), labelled::to_factor)
```

```{r echo = F}
##For the 3 vignettes, if all 3 comprehension questions were correct, a 1 is saved into a string variable names UR01_01 (otherwise it remains empty)

df$isCorrect = 0

#if it's I then the correct response is 2
#otherwise correct response is 1 
for (i in 1:nrow(df)){
    
    whichI <- gregexpr("I", df$Condition_order[i])[[1]][1]
    whichCond <- substr(df$Name_order[i], whichI, whichI)
    
    if (whichCond == "G"){
        df$isCorrect[i] <- df$VG03[i] == 2 & df$VD03[i] == 1 & df$VE03[i] == 1
    } else if (whichCond == "D") {
        df$isCorrect[i] <- df$VG03[i] == 1 & df$VD03[i] == 2 & df$VE03[i] == 1
    } else if (whichCond == "E"){
        df$isCorrect[i] <- df$VG03[i] == 1 & df$VD03[i] == 1 & df$VE03[i] == 2
    }
    
}

df$lab_ID <- toupper(df$lab_ID)

samplesize <- as.data.frame(table(df$isCorrect, df$lab_ID, useNA = "ifany"))
samplesize <- pivot_wider(samplesize,
            id_cols = Var2,
            names_from = Var1,
            values_from = Freq)
colnames(samplesize) <- c("Lab_ID", "Unusable", "Usable", "Missing")
colnames(all_rows) <- c("Lab_ID", "All_Rows")
samplesize <- merge(samplesize, 
                    all_rows,
                    by = "Lab_ID")
samplesize$No_Name <- samplesize$All_Rows - samplesize$Unusable - samplesize$Usable - samplesize$Missing
samplesize <- samplesize[ , c(1, 5, 6, 4, 2, 3)]
#cols <- c("Name_order", "Condition_order", "VD03", "VE03", "VG03", "isCorrect")
#View(df[ , cols])
```

```{r echo = F, eval = F}
for (lab in unique(df$lab_ID)){
  write.csv(subset(df, lab_ID == lab), 
            file = paste0("../docs/data/", lab, ".csv"), 
            row.names = F)
}
```

The number of usable subjects for each lab is presented below.

- All Rows is the number of rows of data that are present in the dataset, which breaks into:
  - No Name indicates the number of test or otherwise unusable rows because a vignette did not get assigned to the participant
  - Missing indicates rows that participants did not complete all the vignette questions, and therefore, are excluded for missing data on those questions
  - Unusable indicates participants that did not answer the comprehension questions correctly
  - Usable participants answered at all three of the comprehension questions on the vignettes correctly

```{r echo = F, results = 'asis'}
ft <- flextable(samplesize)
ft <- fontsize(ft, size = 15, part = "all")
ft <- autofit(ft)
ft
```

```{r eval = F}
print_lab_links <- "<ul> "

for (lab in unique(sort(df$lab_ID))){
  print_lab_links <- paste0(print_lab_links, 
                           "<li>", "<a href='data/", lab, ".csv'> ",
                           lab, "</a>")
}

print_lab_links <- paste0(print_lab_links, "</ul>")
```
