---
title: "ACREP Analysis"
date: "Last Updated: `r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

valid is who answered comp questions correctly 

[Codebook](https://docs.google.com/spreadsheets/d/1KjXqgfVgguHeDXVtlHHhJ9zsRGVDfPVPH4tbh75P46U/edit#gid=903093128)

[Preprint](https://psyarxiv.com/zeux9/)

## Libraries

```{r}
library(lme4)
library(lmerTest)
library(MuMIn)
```

## Import the Data

The `full_long` dataset includes all participants in long format - wherein each trial of their study is on one row of the dataset. Our uploaded data also includes `full.Rds` which is the same data in wide format - one column for each variable in the dataset and one row per participant.

```{r}
readRDS("full_long.Rds")
#str(full_long)
```

## Compute Variables

In this section, we break apart the vignette variable so we know which vignette is tied to each line of data to use in our multilevel analysis. 

```{r}
full_long$vignette <- NA
full_long$vignette[full_long$name_order != "" & !is.na(full_long$name_order)] <- unlist(strsplit(paste0(full_long$name_order[!duplicated(full_long$id) & full_long$name_order != "" & !is.na(full_long$name_order)], collapse = ""), ""))
```

## Data Exclusions

Participants in any laboratory must be excluded for any one of the following reasons: 

(1) if the participant is not the majority age of their country or older (unless parent/guardian waiver provided)

In this section, we will exclude all participants who are under 18 or are not the majority age of their country or older. ***CLARIFY*** anyone less than 18 or just generally not the majority age? What do we mean by majority age? 

Country use lab ID or by the country variable? 

```{r}
summary(full_long$age)
tapply(full_long$age, full_long$lab_id, min, na.rm = T)

# number of rows
nrow(full_long)
# number of participants
length(unique(full_long$id))

valid_data <- subset(full_long, age >= 18)

# number of rows
nrow(valid_data)
# number of participants
length(unique(valid_data$id))
```

(2) if the participant has taken part in a previous version of this study or in another contributors' replication of the same study

***CLARIFY*** this will need to be hand coded 

```{r}
# pull in dictionary 
# subset using dictionary 

# number of rows
nrow(valid_data)
# number of participants
length(unique(valid_data$id))
```

(3) if the participant fails to answer comprehension questions correctly

```{r}
valid_data$urn1 <- factor(valid_data$urn1, levels = c("", "1"), labels = c("Not included", "Included"))
summary(valid_data$urn1)

valid_data <- subset(valid_data, urn1 == "Included")

# number of rows
nrow(valid_data)
# number of participants
length(unique(valid_data$id))
```

(4) if the participant correctly and explicitly articulate knowledge of the specific hypotheses or specific conditions of this study when answering the funneled debriefing questions. 

***CLARIFY*** this will need to be hand coded 

```{r}


# number of rows
nrow(valid_data)
# number of participants
length(unique(valid_data$id))
```

We will also exclude participants who self-report their understanding of the tested language as "not well" or "not well at all". We based this exclusion criteria on a recent study that found that non-native English speakers who self-report as "very well" and "well" tend to score in the "intermediate" and "basic" categories on an English proficiency test respectively, while those who self-report as "not well" and "not at all" tend to score in the "below basic" category (Vickstrom, Shin, Collazo, & Bauman, 2015). All excluded data will be included in the data files on the overall OSF page, along with the particular reason for why they were excluded. 

```{r}
summary(valid_data$language)

valid_data <- subset(valid_data, language != "not very well" | language != "not well at all" | language != "Not answered")

summary(valid_data$language)

# number of rows
nrow(valid_data)
# number of participants
length(unique(valid_data$id))
```

## Descriptive Statistics

In total, [X] labs applied to participate in this multilab replication. [X] labs were unable to participate, [X] did not collect enough data; [X] dropped out prior to data collection, resulting in a final lab count of [X]. Contributing labs represent [X] continents ([X from Africa, X from South America, X from North America, X from Asia, X from Europe, and X from Oceania) with participants residing in [X] countries [X from Brazil, X from Switzerland, X from Singapore, and so on]. [X labs committed to collecting the minimum participant sample size (N = 40), and X labs committed to collecting a larger, more representative sample (N = 100) for the purposes of exploratory analyses. 

```{r}

# number of labs - final
length(unique(valid_data$lab_id))

# number of participants for each lab
table(valid_data$lab_id[duplicated(valid_data$id)])
```

## Analysis

### Knowledge

```{r}
knowledge_model <- glmer(var_know_bin ~ cond + (1 | vignette) + 
                           (1 | lab_id) + (1 | lab_id / id), 
                         data = valid_data,
                         family = binomial, 
                         control = glmerControl(optimizer = "bobyqa"),
                         nAGQ = 1)

summary(knowledge_model)

table(valid_data$cond, valid_data$var_know_bin)

r.squaredGLMM(knowledge_model)
```

### Reasonableness Attribution

```{r}
reason_model <- lmer(var_know_vas ~ cond + (1 | vignette) + 
                           (1 | lab_id) + (1 | lab_id / id), 
                    data = valid_data,
                    na.action = "na.omit")

summary(reason_model)

emmeans(reason_model, "cond")

r.squaredGLMM(reason_model)
```

