---
title: "ACrep_Results.Rmd"
author: "Hannah Moshontz"
date: "Last Updated `r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

*Questions*
- Need to double check that we do not know the order of binary variables within person in the Qualtrics data (and document)
- For binary order, what is "normal" and what is "swapped"? (asked here: https://psych-sci-accelerator.slack.com/archives/C029HKSQAUU/p1638471460121200?thread_ts=1636489085.046400&cid=C029HKSQAUU)
- Portuguese lab swapped directions
- Last lab could be added to the data?
- Why is the age exclusion SO extreme? Many labs mostly collected data from people younger than the age of consent in their country.
- Something is happening with age. A lot of improbably values (mentioned here: https://psych-sci-accelerator.slack.com/archives/C029HKSQAUU/p1638486797125900)
- Is it accurate to say that participants had to correctly answer *all* comprehension questions? What if it was for the Julie / bonus vignette? And were the comprehension questions the correct answer (e.g., Darrel was looking at a red ground squirrel) or also whether Darrel was right or wrong?
- In SSS, were people asked how well they understood English, or how well they understood the language the survey was in?
- I'm not seeing random slope on condition. Do we have an estimate of heterogeneity of the effect by site/lab?

## Purpose

This script generates text for the results section of the ACREP / PSA004 Stage 2 RRR. It also runs the analysis .Rmd.

```{r}
library(janitor)
library(stringr)
library(kableExtra)
library(countrycode)
library(ISOcodes)
```


# Run the analysis script

```{r, child = '../05_Analysis/ACrep_Analysis_V2.Rmd', results = FALSE}
```

# EDA on the analysis set

```{r}
final_long %>% 
  glimpse()
```


A few notes about variables that will be moot when we complete the codebook:
- Person is a unique lab identifier (identifies PI)
- lab_id is a not a unique lab identifier, but rather identifies the undergraduate PI
(and some of these undergraduate PIs were students with the same lab PI)
- lab_country is the variable we are using to identify country/region
- UN_Region groups lab country into larger regions
- source identifies the method of data collection
- id uniquely identifies each participant by concatenating the source (qualtrics vs socscisurvey),
undergraduate PI (lab_id), and the unique identifier (case, which was of a different format depending on source)
- variables ending in valid are logical and identify valid cases (in the "final_long" dataset, there will not be variance)
- variables ending in order indicate the order in which vignettes or condition were presented (varies by participant),
or the order in which binary DVs were presented (for socscisurvey, this varies by person within lab such that people 
were presented with "normal" (*not sure what direction this is*) or "swapped", but for Qualtrics, this was randomized 
within person and so is coded as "mixed" and and we do not have more detailed information about order in the final dataset. also one lab didn't properly randomize.)
- 2104 N are missing age. are these likely test observations? and so this exclusion and over 100 were a way to try to catch the test observations.

# Planned Analyses


```{r}

#labs that applied
n_labs_applied <- 62
n_labs_rejected <- 0
n_labs_failed <- 10

#create dataset for demographics
final_demographics <- final_long %>% 
  group_by(id) %>%
  slice(1) %>% 
  ungroup() %>% 
  select(id, 
         source,
         contains("exclusion"),
         survey_lang,
         turk,
         language,
         lab_id, 
         Person,
         lab_country,
         country,
         UN_Region,
         gender, 
         gender_other,
         starts_with("ethn_"),
         education,
         education_level,
         starts_with("comp"),
         birth_country,
         case,
         age)

full_demographics <- full_long %>% 
  group_by(id) %>%
  slice(1) %>% 
  ungroup() %>% 
  select(id, 
         source,
         contains("exclusion"),
         survey_lang,
         turk,
         language,
         lab_id, 
         Person,
         lab_country,
         country,
         UN_Region,
         gender, 
         gender_other,
         starts_with("ethn_"),
         education,
         education_level,
         starts_with("comp"),
         birth_country,
         case,
         age)

#error out if count doesn't match
if (length(unique(final_long$id)) != nrow(final_demographics)) STOP

```


In total, `r n_labs_applied` labs applied to collect data as part of this multilab replication. Prior to exclusions, `r length(unique(full_demographics$Person))` unique data collection sites contributed data to the project. Sometimes, multiple student researchers from the same lab collected data at the same data collection site (e.g., using the same university subject pool). Data collection sites were located in `r length(unique(full_long$lab_country)` countries spanning world regions (i.e., `r count(group_by(full_long, UN_Region)) %>% drop_na() %>% arrange(-n) %>% pull(UN_Region) %>% paste(collapse = ", ")`). `r n_labs_failed` labs that applied to participate and were approved to collect data did not contribute data to this project, either because they did not collect any data (e.g., due to Covid-19 related campus closures) or because data were collected in a way that rendered them unsuable for these analyses (e.g., data were collected in Qualtrics and the response options were on a different scale or the raw data were deleted). 

The deidentified raw data without any exclusions is available at osf.io/XXXX. Of the `r nrow(full_demographics)` participants who completed the survey, data from `r nrow(full_demographics) - nrow(final_demographics)`% (_n_ = `r`) of people were excluded. 

Specifically, data were excluded for the following pre-registered reasons:
(1) the participant was not the majority age of their country or older (_n_ = `r nrow(filter(full_demographics, age_exclusion)`); operationalized as at least 18 in all countries except Slovakia (where the age of consent is 19) and United Arab Emirates (where the age of consent is 21));
(2) the participant had taken part in a previous version of this study or in another contributors' replication of the same study (_n_ = `r nrow(filter(full_demographics, previous_exclusion)`;as evaluated by three human coders, as described in Supplement X, Section X);
(3) the participant failed to answer all comprehension questions correctly (_n_ = `r nrow(filter(full_demographics, studyans_exclusion)`; e.g., did not correctly identify what Darrel was looking at in the vignette);
(4) the participant correctly and explicitly articulated knowledge of the specific hypotheses or specific conditions of this study when asked what they thought the study hypothesis was (_n_ = `r nrow(filter(full_demographics, purpose)`; as evaluated by three human coders, as described in Supplement X, Section X);
(5) the participant reported their understanding of the language the survey was written in as "not well" or "not well at all" (_n_ = `r nrow(filter(full_demographics, lang_exclusion)`; see Vickstrom, Shin, Collazo, & Bauman, 2015). 

No additional exclusions were described in our approved protocol. However, after pre-registered exclusion criteria, there appeared to be invalid test responses in the data (e.g., the word "test" was written in response to open-ended questions). No clear method was devised to identify test responses, but, at many data collection sites, the students and other researchers executing the study tested their survey link multiple times, resulting in invalid survey observations. The following exclusions were designed to remove these invalid test observations using consistent, reliable criteria that related to a covariate: Data were excluded if the participant did not provide an age (_n_ = `r nrow(filter(full_demographics, is.na(age)))`) or listed an age greater than or equal to 100 (_n_ = `r nrow(filter(full_demographics, !(age < 100)))`).

In the analysis sample (i.e., following exclusions), participants were `r nrow(final_demographics)` adults recruited to participate by student researchers at `r length(unique(final_long$Person))` data collection sites in `r length(unique(final_long$lab_country)` countries spanning world regions (i.e., `r count(group_by(final_long, UN_Region)) %>% drop_na() %>% arrange(-n) %>% pull(UN_Region) %>% paste(collapse = ", ")`). Data collection sites contributed an average of `r final_demographics %>% group_by(Person) %>% count() %>% pull(n) %>% mean() %>% round(2)` participants to the anlaysis sample (min = `r final_demographics %>% group_by(Person) %>% count() %>% pull(n) %>% min()`, max = `r final_demographics %>% group_by(Person) %>% count() %>% pull(n) %>% max()`). See Table X for a summary of participants' age, years of education, and ethnic/racial identity.

Participation details, like compensation, varied by data collection site, as summarized in Table X and Table X. In the approved protocol, we planned to collect all data using a single SocSciSurvey survey programmed to accomodate lab-specific variations. However, some used Qualtrics surveys that student researchers programmed themselves. Most data collection sites used the central SocSciSurvey survey.

```{r}
final_demographics %>% 
  select(age, education) %>% 
  describe() %>% 
  .[1:2,c(2,3,4,8,9)] %>% 
  kable(digits = 2) %>% 
  kable_styling()
```

In the approved proposal, we planned to measure participants' racial and ethnic identities using an open-ended response. For reasons that were not documented, racial and ethnic identity was measured using non-exclusive cateogories with an open-ended fill-in option. Student research teams designed different response options tailored to their geographic region (see all variations in Supplemental Table X). All data collection sites allowed people to select multiple racial and ethnic identities, and all asked whether participants identified as White (either "White/European", "White / European descent", or "European descent"). In the final sample, `r`% (_n_ = `r`) identified as one of these 


*One version in SSS had these response options:*
White / European descent
Black / African descent
Latino*a / Latin American descent
Australian descent
Asian
Southeast Asian descent
Native American
Hawaiian descent / Pacific Islands
Other

*The other version in SSS had these response options:*
European descent
African descent
Latino*a / Latin American descent
Indigenous Australian or Torres Strait Islander descent
East Asian descent
South Asian descent
Pacific Island descent
Native American descent

*In Qualtrics these were the response options:*
White/European
Black/African American
Hispanic Latino
East or Southeast Asian / Pacific Islander (e.g. from Japan, China, Korea, Vietnam, Thailand, Philippines, native Hawaiian)
South Asian (e.g. from India, Pakistan)
I prefer not to answer this question
Other

```{r}
#Qualtrics labs combined categories, and had a south asian category, but had no positive cases
#combining those here such that false responses are coded as false for each cateory
final_demographics$ethn_as[final_demographics$ethn_as_sea_pac == FALSE] <- FALSE
final_demographics$ethn_as[final_demographics$ethn_sa == FALSE] <- FALSE
final_demographics$ethn_sea[final_demographics$ethn_as_sea_pac == FALSE] <- FALSE
final_demographics$ethn_pac[final_demographics$ethn_as_sea_pac == FALSE] <- FALSE

final_demographics %>% 
  select(contains("ethn_")) %>% 
  mutate(across(.cols = everything(), ~as.numeric(.x))) %>% 
  select(-ethn_other_text,
         -ethn_none, -ethn_sa) %>%  #Qualtrics labs added a 'prefer not to say' response option
  describe() %>% 
  .[,c(2,3,4,8,9)] %>% 
  mutate(count = n*mean,
         percent = count/n*100) %>% 
  select(n, count, percent, everything()) %>% 
  kable(digits = 2, caption = "Number and Percent of Participants Self-Identified with each Ethnic or Racial Category)") %>% 
  kable_styling()

```


```{r}
final_demographics %>% 
  select(comp, turk, source) %>% 
  mutate(source = as.factor(source)) %>% 
  mutate(across(.cols = everything(), ~as.numeric(.x))) %>% 
  mutate(comp = comp - 1,
         `Took the centralized survey` = source - 1) %>%  #adjusting numeric values so 0 is no and 1 is yes
  select(-source) %>% 
  rename(`Recruited through Mturk` = turk,
         `Compensated for participation` = comp) %>% 
  describe() %>% 
  .[,c(2,3,4,8,9)] %>% 
  mutate(count = n*mean,
         percent = count/n*100) %>% 
  select(count, percent) %>% 
  kable(digits = 2, caption = "Number and Percent of Participants by Data Collection Context Variables (Total N = 2957)") %>% 
  kable_styling()

```


```{r}
final_demographics %>% 
  mutate(lab_country_full = countrycode(lab_country, "iso3c", "country.name.en")) %>% 
  tabyl(lab_country_full) %>% 
  arrange(-n) %>% 
  kable(digits = 2, caption = "Number and Percent of Participants by Country") %>% 
  kable_styling()
```

```{r}
survey_lang_table <- final_demographics %>%
  mutate(survey_lang = str_replace_all(survey_lang, "prt", "por"),
         survey_lang = str_replace_all(survey_lang, "zho", "chi")) %>% 
  tabyl(survey_lang) %>% 
  arrange(-n)

for (i in 1:length(survey_lang_table$survey_lang)) {
  
  survey_lang_table$survey_lang[i] <- ISO_639_2$Name[ISO_639_2$Alpha_3_B == survey_lang_table$survey_lang[i]]
  
}

survey_lang_table %>% 
  mutate(survey_lang = str_replace_all(survey_lang, "Greek, Modern \\(1453\\-\\)", "Greek"),
         survey_lang = str_replace_all(survey_lang, "Romanian; Moldavian; Moldovan", "Romanian")) %>% 
  kable(digits = 2, caption = "Number and Percent of Participants by Survey Language") %>% 
  kable_styling()
```


## Procedure

Data collection took place between January 1, 2019 and June 1, 2021. Some participants completed the study survey from a campus laboratory. All participants completed an online survey that included a consent form. After providing informed consent, participants read and answered questions about three vignettes whose content and conditions varied according to the random presentation feature in SocSciSurvey and Qualtrics. The vignettes used in the study were selected on the basis of pretesting in English, described in Appendix X. 

Vignette content varied by subject and identification target. In one scenario, Darrel identified prarie dogs vs red speckled ground squirrels (cite original). In another scenario, .... In a third scenario, .... Some student researchers opted to include a fourth scenario that was not included in the present analyses but can be found in Appendix X. 

After each vignette, participants evaluated: 1) whether the subject believes or knows, measured either on a continuous scale from 0 to 100 or as a binary choice;
2) the true correct answer, which functioned as a comprehension question and was measured as a binary choice between the two identification options;
3) the extent to which the subject's belief was unreasonable or reasonable, measured either on a continuous scale from 0 to 100 or as a binary choice;
4) whether or not the subject correctly identified the target.

*Obvious mistakes in entering data*


# Disclosures


*Data, materials, and online resources:* All data are posted publicly on our master OSF page (https://osf.io/n5b3w/), and each contributing site has posted their data on an OSF page linked to our master OSF page.


## Reporting

 “We report how we determined our sample size, all data exclusions, all manipulations, and all measures in the study” (see Simmons, Nelson, & Simonsohn, 2011).
 
## Ethical approval 

All contributing labs were required to submit their local institutional ethics approval prior to data collection as part of their pre-registstration and CREP review process and will be carried out in accordance with the provisions of the World Medical Association Declaration of Helsinki. All participating labs posted their ethics approval to their lab's OSF page for this study. 

## Author Contributions

Authorship implies significant participation in the research reported or in writing the manuscript, including participation in designing and/or interpreting reported experiments or results, participation in acquiring and/or analyzing data, or participation in drafting and/or revising the manuscript. All authors must agree to the order in which the authors are listed and must have read the final manuscript and approved its submission. They must also agree to take responsibility for the work in the event that its integrity or veracity is questioned. In complete sentences, authors should precisely describe their contributions to the research and manuscript, identifying each author by his or her initials and surname. For example: “D. J. Simons and A. O. Holcombe jointly generated the idea for the study. A. O. Holcombe programmed the study and collected the data. D. J. Simons wrote the analysis code and analyzed the data, and A. O. Holcombe verified the accuracy of those analyses. D. J. Simons wrote the first draft of the manuscript, and both authors critically edited it. Both authors approved the final submitted version of the manuscript.”

## Conflicts of Interest

The author(s) declare that there were no conflicts of interest with respect to the authorship or the publication of this article.

## Acknowledgments

Authors should use this section to identify any people who should be credited for their assistance with the reported research.

## Funding

This section should be used to acknowledge funding sources, in complete sentences and with the full names of funders spelled out.
    
## Supplemental Material

If Supplemental Material will be posted on the journal’s Web site, include this heading and the appropriate link will be added during editing.

## Prior versions

If part or all of a submitted manuscript was previously posted to a blog or to a preprint archive, the authors should provide a link to that source and briefly indicate what aspects of the submitted manuscript are shared with that prior version.
